| Base de datos de abejas Ibéricas \n| Iberian Bees database\n

### 2022-03-17 Manuscript/manuscript.Rmd
to check file updated

###### TABLA 1

@@

@@

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../Data/Metadata/attributes.csv")
kable(metadata[,-1])
```

>>>>

\newpage

###### LEYENDA DE TABLA

@@

###### TABLE CAPTION

@@

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../Data/Metadata/attributes.csv")
colnames(metadata) <- c("Variable name", "Description", "Data type")

kable(metadata[,-1])
```

\newpage
